INGRID: Creating Languages in MPS from ANTLR Grammars

### 2016-11-08 chapters/conclusion.tex
conclusion

\todo{Write something.}

There is lot of further follow-up work to be done. Many open problems remain.

Automated generation of the editor aspect, probably using some kind of machine learning.
Generating nicely designed and user-friendly editors, maybe using artificial intelligence (machine learning) that would evaluate (analyze) existing code in plain text and based on that create the editors.

Follow-up work might look more into the problem of code layout detection, possibly exploring suggested approaches such as the learning approach described in Section XY \todo{Tohle se snad podari aspon castecne implementovat}.
This could lead to better results in editor and TextGen aspect generation which could definitely use some improvement.
Another future endeavors will definitely touch the subject of generating parsers that would enable the user to import existing source code into MPS.

>>>>

Our contribution is the INGRID method for constructing language definitions in MPS from their grammars in the ANTLR notation.
The method is only partially automated, but nevertheless it greatly reduces the amount of manual work that developers of MPS languages have to perform.
Although we discussed all the challenges, details of our solution and general observations just in the context of ANTLR grammars and JetBrains MPS, we believe they are more general --- and in particular relevant to everyone tackling a similar problem in the field of DSLs and language workbenches.

In the future, we would like to address the remaining open problems (there are many of them) and increase the level of automation.
Our primary research goal is to investigate the usage of machine learning for the purpose of generating editors that support nice and readable code layout.
The information about code layout, once it is available, will be then leveraged and used also to improve TextGen.
Another subject for future work is generating parsers that would allow users to import existing source code into MPS.
